
% Define the fields for this entry
\expPosTitle{Research Assistant}
\expPosPeriod{Nov 2009 -- Dec 2017}
\expOrgName{\href{http://sefcom.asu.edu/}{Security Engineering for Future Computing (SEFCOM)
Lab}\iftoggle{fullAddress}{}{, ASU}}
\expOrgLoc{\iftoggle{fullAddress}{699 S Mill Ave Ste 553, Tempe, AZ 85281}{Tempe, AZ}}
\expExtra{\textit{Lab Directors:} Gail-Joon Ahn, Adam Doup\'{e}, Ziming Zhao, Yan Shoshitaishvili%
  \iftoggle{superInfo}{\\ \textit{Supervisor:} Gail-Joon Ahn, (704)~517-0707, \mailto{gahn@asu.edu}}{%
  \rResumeOnly{\\ \textit{Sponsors}: Department of Energy, National Science Foundation}}% CV lists sponsors down below
  }


\begin{rExperience}

  \rCVonly{ % CV gives a list of projects

    \item Projects:

      \begin{rBulletList}

        \item Designed a framework for conducting forensics on web environments that addresses the unique challenges
          forensic examiners face in this domain.\rCVonly{\\
          \emph{Publications:}~\cite{MabeyIFIP}}
  }

        \item Implemented a forensic tool in \textbf{Python} that uses the G~Suite APIs as a proxy for analyzing
          encrypted \textbf{Chromebooks} to reconstruct the timeline of events of an incident.

        \item Created a method for identifying extensions installed on \textbf{Chrome~OS} by analyzing the encrypted
          files on the hard drive. Wrote an accompanying crawler in \textbf{Python} (and using \textbf{Ansible},
          \textbf{Celery}, \textbf{MySQL}, \textbf{sshfs}, and \textbf{OpenStack}) to download all extensions on the
          Chrome Web Store and analyze them.\rCVonly{\\
          \emph{Publications:}~\cite{MabeyDFRWS, IASymp_Mabey2015, MabeyBlogCheckout2016, MabeyBlogFixRepo2015}}

        \item Helped design and implement a cloud-based version of the International Capture the Flag (iCTF)
          competition, allowing educators to more easily host their own CTF competitions. Used \textbf{Ansible},
          \textbf{Vagrant}, \textbf{Amazon EC2}, and \textbf{Python} for the implementation and deployment.\rCVonly{\\
          \emph{Publications:}~\cite{Trickel2017}}

        \item Developed a forensic acquisition approach for web email that reestablishes persistent cookie sessions
          stored by a browser, and automated the process using \textbf{Python} and \textbf{Selenium}.\rCVonly{\\
          \emph{Publications:}~\cite{Paglierani2013}}

        \item Designed and implemented the core components of a modular, highly scalable, collaboration-centric digital
          forensic framework built on the \textbf{OpenStack} cloud architecture. Functions of the components included
          distributed job scheduling, storage management, and concise evidence representation and
          transmission.\rCVonly{\\
          \emph{Publications:}~\cite{Mabey2011, Mabey2013, IAWS_Mabey2012}}

  \rCVonly{

      \end{rBulletList}

    \item Other experience:
      \begin{rBulletList}
  }

        \item Maintained fifteen servers for the lab, including a public-facing router, an \textbf{OpenVPN} server, a
          reverse-proxy web server with \textbf{TLS} certificate management, an \textbf{OpenStack} cloud, switches
          transmitting \textbf{VLAN}-tagged traffic, and a \textbf{GitLab} server.

  \rCVonly{

        % \item Acted as a mentor for an undergraduate student that otherwise would not have pursued a master's degree and
          % collaborated with him on the research for his thesis.

      \end{rBulletList}

    \item Sponsors:
      \begin{rBulletList}[2]

        \item Department of Defense Information Assurance Scholarship Program (IASP)

        \item Department of Energy

        \item National Science Foundation

      \end{rBulletList}

  }

\end{rExperience}
