% Define the fields for this entry
\expPosTitle{Backend Engineer 3 - Product}
\expPosPeriod{Jul 2019 -- Jul 2023} % Remember to use -- between dates
\expOrgName{Cedar Cares, Inc.}
\expOrgLoc{Salt Lake City, UT}
% \iftoggle{superInfo}{
  \expExtra{%
  \textit{Supervisor:}\; Tristan McCormick\;\; (651) 494-8503\;\; \mailto{tristan@cedar.com}}
% }{}


\begin{rExperience}

  \item Initially hired by OODA Health, Inc., which was acquired by Cedar in Jun 2021.

  \item Authored and open-sourced \href{https://github.com/cedar-team/pyredox}{\texttt{pyredox}}, a \textbf{Python}
    library that aids in parsing, validating, and generating JSON payloads for communicating with
    \href{https://www.redoxengine.com/}{Redox Engine}, a clinical data broker.
    % platform designed to connect providers, payers, and products.

  % \item Implemented tools for health insurance companies to review claims and prior authorization requests that
    % identified, parsed, and presented the relevant clinical information to decrease the time needed to process and
    % adjudicate requests.

  \item Used \textbf{Domain-Driven Development} (DDD) patterns while refactoring a batch-based \textbf{Python} service
    to be event-based, reducing client data refresh times from 30 minutes (average) down to a few seconds.

  \item Implemented tools that identified, parsed, and presented clinical information relevant to claims and prior
    authorization requests to decrease the time needed for
    % health insurance companies
    payers
    to process and adjudicate
    requests. Technologies used include \textbf{Python}, \textbf{gRPC}/\textbf{protobufs}, AWS (\textbf{EC2},
    \textbf{SQS}, \textbf{S3}, and \textbf{KMS}), \textbf{MariaDB}/\textbf{Postgres}, \textbf{OpenCV}, \textbf{OAuth},
    as well as the X12 \textbf{EDI} and \textbf{FHIR} data formats.

  \item Led the effort to integrate with two electronic health record (EHR) systems, Cerner and Epic, using the
    FHIR specification; included acting as technical point-of-contact during certification by Cerner.

  \item Implemented many \textbf{ETLs} in \textbf{Python} for transforming external data to match internal structures
    and vice versa.

  \item Wrote \textbf{Swagger} documentation for customers connecting to our API implemented in \textbf{FastAPI}.

  % \item Contributed to the open-source \href{https://github.com/nazrulworld/fhir.resources}{\texttt{fhir.resources}}
    % Python library to include support for the DSTU2 version of the FHIR spec, which was necessary to complete the EHR
    % integrations mentioned above.

\end{rExperience}

