
% Define the fields for this entry
\expPosTitle{Computer Scientist (U.S.~Army Civilian)}
\expPosPeriod{Dec 2017 -- Jun 2019} % Remember to use -- between dates
\expOrgName{Data Science Directorate, Network Enterprise Technology Command~(NETCOM)}
\expOrgLoc{\iftoggle{fullAddress}{6201 E Oak St, Phoenix, AZ 85008}{Phoenix, AZ}}
\expExtra{\threecol{\textit{Grade}: GS-0854-12 Step 1}{\textit{Service}: Competitive}{\textit{Tenure}: Conditional, Full-Time}%
  \iftoggle{superInfo}{%
  \\ \textit{Supervisor:} Jerrie Core, (719)~317-3108, \href{mailto:jerrie.l.core.civ@mail.mil}{jerrie.l.core.civ@mail.mil}}{}%
}


\begin{rExperience}

  \item Designed, implemented, and deployed analytics for the Army's instance of DISA's \textbf{Big Data
    Platform~(BDP)}, including an app for monitoring vulnerability patching compliance and a dashboard for visualizing
    performance of information technology service management (ITSM) ticket resolution. Analytics were composed of a web
    interface using \textbf{Python}, \textbf{Flask}, \textbf{Vue}, and \textbf{Bootstrap}, with \textbf{pandas} for the
    data analysis, \textbf{Plotly} for the visualizations, and \textbf{Celery} and \textbf{redis} for task management.

  \item Shortened the development cycle for BDP apps by automating the build, packaging, and deployment process using
    \textbf{Python} and GitLab's \textbf{Continuous Integration} utility.

  \item Acted as technical liaison during fiscal year 2018 for a \$3 million contract with Sandia National Laboratories
    to implement tools such as an anomaly detection ensemble, an emulation model of a notional network, and a WHOIS
    registrant analyzer. I acquired data samples to inform the implementation and testing of the analytics, ensured the
    projects stayed focused on operational objectives, held weekly sync meetings, reported to leadership on Sandia's
    progress, and assessed the value of the delivered products.

  \item Technical lead for NETCOM Data Science with ASU. Led strategic discussions with ASU's Global Security
    Initiative~(GSI) leadership to collaborate on real-world NETCOM issues. Spearheaded the effort for ASU to gain
    access to an instance of the Army's BDP for improved technical collaboration. Served as the Army's program lead for
    the ASU Computer Science Capstone initiative.

  \item Initiated a culture in the Directorate of using \textbf{git}, \textbf{GitLab}, and DevOps methods and
    established internal best practices for collaborating on code development and documenting lessons learned.

\end{rExperience}
