%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.75in]{geometry} % Document margins

% Set font to sans serif
\renewcommand*{\familydefault}{\sfdefault}

\usepackage{multicol} %columns for lists
\usepackage{paralist} %lists without indentation
\usepackage{hyperref} %links - http and mailto
\hypersetup{hidelinks} %hide boxes around links
%check out other hyperref options

\usepackage{microtype}

\setlength\multicolsep{0pt} %remove space before and after multicol

\def\sectionskip{\smallskip} % The space after the heading section
\def\nameskip{\medskip} % The space after your name at the top
\def\addressskip{} % The space between the two address (or phone/email) lines

\name{Michael K. Mabey} % Your name
\address{(480)~788--3411 \\ \href{mailto:mmabey@asu.edu}{mmabey@asu.edu}} % Your phone number and email
\address{5606 S Hurricane Ct Unit E \\ Tempe, AZ 85283} % Your address
%\address{\href{https://jpaglier.blogspot.com}{https://jpaglier.blogspot.com} \\ %\href{https://www.bitbucket.org/jpaglier}{https://www.bitbucket.org/jpaglier}} %blog and bitbucket

\icon{0.5in}{LinkedInQR}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{PhD Computer Science (Information Assurance)}\hfill \emph{May 2016}\\
Arizona State University $\mid$ GPA 3.81\hfill {Tempe, AZ}

\textbf{M.S. Computer Science (Information Assurance)}\hfill \emph{Aug 2011}\\
Arizona State University $\mid$ GPA 3.58\hfill {Tempe, AZ}\\
\textbf{Thesis:} \href{http://repository.asu.edu/attachments/56996/content/Mabey_asu_0010N_10959.pdf}{Collaborative Digital Forensics: Architecture, Mechanisms, and Case Study}

\textbf{B.S. Computer Science (Information Systems)}\hfill \emph{May 2009}\\
Utah State University $\mid$ GPA 3.25\hfill {Logan, UT}

%\textbf{Relevant Coursework}
%\begin{multicols}{2}
%	\begin{asparaitem} \itemsep1pt \parskip0pt \parsep0pt
%		\item Computer System Security
%		\item Data and Information Security
%		\item Software Security
%		\item Advanced Computer Network Security
%		\item Computer and Network Forensics
%		\item Embedded Operating System Internals 
%		\item Advanced Operating Systems
%	\end{asparaitem}
%\end{multicols}

\end{rSection}


%----------------------------------------------------------------------------------------
%   COURSE PROJECTS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Course Projects}
%
%\begin{asparaitem} \itemsep1pt \parskip0pt \parsep0pt
%	\item \href{https://bitbucket.org/jpaglier/cse536-kernel-dev}{Distributed messaging service with accompanying kernel-level transport protocol \hfill (Linux, C)}
%	\item Web-based document management system \hfill (Java, Struts2, Tomcat 6, Linux, MySQL)
%	\item Cloud-based file sharing protocol and application \hfill (Linux, Python)
%	\item \href{https://bitbucket.org/jpaglier/2012-spring-cse494-598_g-project}{Volume and file system analysis tool with an emphasis on FAT systems \hfill (Python)}
%	\item Build a secure network containing Apache and bind servers \hfill (iptables, Squid, Snort)
%	\item Database system supporting access control and k-anonymity functionality \hfill (Java, MySQL)
%	\item Smart sprinkler controller system using an embedded platform \hfill (Linux, cron, Apache, C/C++)
%\end{asparaitem}
%
%\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%\begin{rSubsection}{1: Company}{2: Dates}{3: Title}{4: Location}
%\end{rSubsection}

\begin{rSubsection}{Research Assistant~}{Nov 2009 -- Present}{\href{http://sefcom.asu.edu/}{Security Engineering for Future Computing (SEFCOM) Lab, ASU}}{Tempe, AZ\\{\textnormal{Advisor: Prof. Gail-Joon Ahn\hfill Sponsors: Department of Energy and National Science Foundation}}}

	\item Developed an approach to acquire a suspect's email from a web client by reestablishing persistent cookie sessions stored by a browser. Wrote an accompanying Python script that used Selenium to then interact with the online email account.
	
	\item Designed and implemented the core components of a modular, highly scalable, collaboration-centric digital forensic framework built on the OpenStack cloud architecture. Functions of the components included distributed job scheduling, storage management, and concise evidence representation and transmission.
	
	\item Set up and maintained a virtual private network (VPN) using OpenVPN for allowing remote access to lab equipment by members of the SEFCOM lab.
	
	\item Acted as a mentor for an undergraduate student that otherwise would not have pursued a master's degree, and collaborated with him on research for his thesis.
	
	\item Researched methods for performing forensic acquisition on Android devices.
	
	\item Leader and deployment point of contact of the 2009 and 2010 ASU teams in the International Capture the Flag competition sponsored by University of California, Santa Barbara.
	
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Aug 2010 -- Present}{Arizona State University}{Tempe, AZ}

	\item Spring 2014: Assistant to Mr. Ryan Meuth for FSE 100 Introduction to Engineering and Dr. Debra Calliss for CSE 423/424 Capstone I and CSE 485/486 Capstone II.
	
	\item Instructor for FSE 100 Introduction to Engineering multiple semesters: Fall 2011, Spring 2012, Fall 2012, Spring 2013, and Fall 2013.
	
	\item Spring 2011: Assistant to Dr. Gail-Joon Ahn for CSE 467 Data \& Information Security.
	
	\item Fall 2010: Assistant to Dr. Gail-Joon Ahn for CSE 465 Information Assurance.
	
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Student Trainee}{June 2013 -- Aug 2013}{US Army}{Fort Meade, MD}


	\item Summer internship in connection with DoD Information Assurance Scholarship Program (IASP) scholarship.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Graduate Student Summer Intern}{May 2011 -- Jul 2011}{Sandia National Laboratories}{Albuquerque, NM}

	\item Helped design a dynamic malware analysis framework built on OpenStack that allowed incident responders to define highly customizable analysis environments and use arbitrary analysis tools in either triage or manual analysis mode.
	
	\item Wrote Python scripts to automate the setup process for using a SheevaPlug computer as a wireless intrusion detection agent running Kismet.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Graduate Student Recruitment Specialist/Webmaster}{Jul 2006 -- Aug 2009}{Electrical \& Computer Engineering Department USU}{Logan, UT}

	\item Primary responsibilities included maintaining and augmenting the department website using PHP, MySQL, and other basic web technologies like CSS, JavaScript, and an SMTP server.
	
	\item Replaced a MS Access database by porting the old data to a MySQL server and creating a set of Python programs with the Dabo framework that interfaced with the database.
	
	\item Wrote Python scripts to convert tab-delimited and Excel formatted data to SQL entries.
	
	%\item Created a testing environment using an Apache web server, PHP, MySQL, and SVN.
	
	%\item Gathered statistics on web visitors, inquiries from students, and applicants' credentials for the purpose of improving graduate student recruitment processes for the department.
	
	\item Responded to inquiries from potential domestic and international graduate students.

\end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{\href{http://sefcom.asu.edu/}{SEFCOM, Arizona State University}}{January 2011 - December 2013}{Research Assistant}{Tempe, AZ}
%
%	\medskip %multicols breaks the spacing for some reason
%	\begin{multicols}{2}
%		\item Develop novel e-mail forensics methodologies
%		\item Conduct  analysis of Android malware
%		\item Create a taxonomy of Android malware
%		\item Deploy and manage a cloud for use in a \\ collaborative forensics platform (OpenStack)
%		\item Prepare  and deliver weekly presentations
%	\end{multicols}
%
%\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Java, Python, C/C++, Ruby \\
Design Patterns & MVC, Service Locator, etc. \\
Protocols \& APIs & XML, JSON, REST \\
Network Administration/Security & Wireshark, iptables, Snort, etc. \\
Operating Systems & Linux, Windows \\
Databases & MySQL, SQLite \\
Tools & Git, Vim
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\bibliographystyle{mikeresume}
\mybibliography{mypapers}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Activities}

\begin{asparaitem} \itemsep1pt \parskip0pt \parsep0pt
	\item National Science Foundation Scholarship for Service \hfill January 2012 - December 2013
	\item \href{http://asulug.org/2013/09/installfest-fall-2013-results/}{\($1$st\) place: State Farm’s ASU Linux User Group CTF \hfill September 2013}
	\item \href{https://code.djangoproject.com/ticket/20760}{Accepted patch: Timing attack in Django authentication module (Ticket \#20760)} \hfill July 2013
	\item Participant –-- UCSB International CTF –-- Arizona State University Team \hfill December 2010
	\item Undergraduate Teaching Assistant – CSE 100 Introduction to Java Programming \hfill Fall 2009
\end{asparaitem}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
