%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%\begin{rSubsection}{1: Company}{2: Dates}{3: Title}{4: Location}
%\end{rSubsection}

\begin{rSubsection}{Research Assistant~}{Nov 2009 -- Present}{\href{http://sefcom.asu.edu/}{Security Engineering for Future Computing (SEFCOM) Lab, ASU}}{Tempe, AZ\\{\textnormal{\textit{Advisor}: Prof.\ Gail-Joon Ahn\hfill \textit{Sponsors}: Department of Energy and National Science Foundation}}}

	\item Recipient of the Department of Defense Information Assurance Scholarship Program (IASP) for the 2012--2013, 2013--2014, and 2014--2015 school years.

	\item Researched forensic techniques for \textbf{Chrome~OS}/\textbf{Chromium~OS} by creating tools in \textbf{Python} and using \textbf{libvirt} to interface with \textbf{KVM/QEMU}. (Project in progress.)

	\item Developed a web email acquisition approach that reestablishes persistent cookie sessions stored by a browser, and automated the process using \textbf{Python} and \textbf{Selenium}~\cite{Paglierani2013}.
	%Wrote an accompanying \textbf{Python} script that used \textbf{Selenium} to then interact with the online email account.

	\item Designed and implemented the core components of a modular, highly scalable, collaboration-centric digital forensic framework built on the \textbf{OpenStack} cloud architecture. Functions of the components included distributed job scheduling, storage management, and concise evidence representation and transmission~\cite{Mabey2011a,Mabey2011}.

	\item Set up and maintained an \textbf{OpenVPN} installation for the SEFCOM lab.

	%\item Researched methods for performing forensic acquisition on \textbf{Android} devices.

	%\item Acted as a mentor for an undergraduate student that otherwise would not have pursued a master's degree and collaborated with him on the research for his thesis.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Aug 2010 -- Present}{Arizona State University}{Tempe, AZ}

	\item[] \vspace{-1.6em}
	\end{list}

	\emph{Instructor positions:}
	\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
		\itemsep-0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
	\item CSE 465 Information Assurance: Fall 2014.
	\item FSE 100 Introduction to Engineering: Fall 2011, Spring 2012, Fall 2012, Spring 2013, and Fall 2013.
	\end{list}

	\emph{Assistant positions:}
	\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
		\itemsep-0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
	\item CSE 469 Computer and Network Forensics with Dr.\ Gail-Joon Ahn: Spring 2015.
	\item FSE 100 Introduction to Engineering with Dr.\ Ryan Meuth: Spring 2014.
	\item CSE 423/424 Capstone I and CSE 485/486 Capstone II with Dr.\ Debra Calliss: Spring 2014.
	\item CSE 467 Data \& Information Security with Dr.\ Gail-Joon Ahn: Spring 2011.
	\item CSE 465 Information Assurance with Dr.\ Gail-Joon Ahn: Fall 2010.

	%\item Instructor for CSE 465 Information Assurance: Fall 2014

	%\item Instructor for FSE 100 Introduction to Engineering: Fall 2011, Spring \& Fall 2012, Spring \& Fall 2013.

	%\item Spring 2014: Assistant to Dr. Ryan Meuth for FSE 100 Introduction to Engineering.

	%\item Spring 2014: Assistant to Dr. Debra Calliss for CSE 423/424 Capstone I and CSE 485/486 Capstone II.

	%\item Spring 2011: Assistant to Dr. Gail-Joon Ahn for CSE 467 Data \& Information Security.

	%\item Fall 2010: Assistant to Dr. Gail-Joon Ahn for CSE 465 Information Assurance.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Student Trainee}{Jun 2013 -- Aug 2013, Jun 2014 -- Aug 2014}{US Army}{Fort Meade, MD}


	\item Summer internships in connection with DoD IASP scholarship.

\end{rSubsection}

%------------------------------------------------
\clearpage

\begin{rSubsection}{Graduate Student Summer Intern}{May 2011 -- Jul 2011}{Sandia National Laboratories}{Albuquerque, NM}

	\item Helped design a dynamic malware analysis framework built on \textbf{OpenStack}, allowing incident responders to define customizable analysis environments and use arbitrary analysis tools in triage or manual analysis mode.

	\item Wrote \textbf{Python} scripts to automate the setup process for using a SheevaPlug computer as a wireless intrusion detection agent running \textbf{Kismet}.

\end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{Graduate Student Recruitment Specialist/Webmaster}{Jul 2006 -- Aug 2009}{Electrical \& Computer Engineering Department USU}{Logan, UT}
%
%	\item Primary responsibilities included maintaining and augmenting the department website using \textbf{PHP}, \textbf{MySQL}, and other basic web technologies like \textbf{CSS}, \textbf{JavaScript}, and an \textbf{SMTP} server.
%
%	\item Replaced a \textbf{MS Access} database by porting the old data to a \textbf{MySQL} server and creating a set of \textbf{Python} programs with the \textbf{Dabo} framework that interfaced with the database.
%
%	%\item Wrote \textbf{Python} scripts to convert tab-delimited and Excel formatted data to \textbf{SQL} entries.
%
%	%\item Created a testing environment using an \textbf{Apache} web server, \textbf{PHP}, \textbf{MySQL}, and \textbf{SVN}.
%
%	%\item Gathered statistics on web visitors, inquiries from students, and applicants' credentials for the purpose of improving graduate student recruitment processes for the department.
%
%	%\item Responded to inquiries from potential domestic and international graduate students.
%
%\end{rSubsection}

\end{rSection}
